Measuring Lattices

### 2023-05-09 MeasuringLattices_uv5016/MeasuringLattices.tex
changes for Mois

@@

>>>>

	\section{Forward}

	"Measuring Lattices" is intended to be a summary of an invited talk
	for satellite meeting, "Mathematics and Computer Science for Materials Innovation: Crystal Lattice Classifications" of August, 2022, ECM33
	meeting (https://www.ecm33.fr/). The intent is describe in brief
	the basics of implementing a metric space that creates
	a measure of the "distances" between lattices.

@@

Crystallographic software delivered with diffractometers, used for processing
beamline data, etc. has produced more than one and quarter million structures. The structures have had internally consistent lattice and
symmetry identification, but there have been serious omissions in 
providing globally consistent lattice and symmetry identification
because of structures being done in the incorrect space group.
\citeasnoun{LeTrong2007} published the case of phospholipase
A2, and more were found in \citeasnoun{McGill2014}.
Not having failed to be observed is quite different from always working. Two regions of the space of lattice determination come into play here. 
First, how much error do we want to consider? For protein work, especially for serial crystallography, the errors can be large. Second, the simple methods commonly used in 
diffractometer software are likely to fail for 
some of the less common cases: centered lattices commonly cause interesting issues; lattices that are needle- or pancake-shaped are often challenging;
the five-fold ambiguity cited by \citeasnoun{Gruber1973} also causes confusion. The cited five-fold ambiguity is only for the particular
case that Gruber listed, but interchanges of the axes to produce
other, Buerger-reduced cells.
